Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-06-26 paper/main.tex
rm old figures, remove color on grant

\textcolor{red}{This work was in part supported by the U.S. Department
of Energy, Office of Science, Office of Advanced Scientific Computing Research, 
Scientific Discovery through Advanced Computing (SciDAC) program through 
Grant 420453 "Enabling Cosmic Discoveries in the Exascale Era."}

>>>>

This work was in part supported by the U.S. Department
of Energy, Office of Science, Office of Advanced Scientific Computing Research, 
Scientific Discovery through Advanced Computing (SciDAC) program through 
Grant 420453 ``Enabling Cosmic Discoveries in the Exascale Era."
